Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2021-03-11 paper/main.tex
general

\begin{IEEEkeywords}
Domotic plugs; ADD MORE HERE
\end{IEEEkeywords}

@@

\section{General architecture}
The architecture implemented differs from the most common architectures used in this scenario in two major aspects, first most homes don't have this kind of system even in place, instead a circuit breaker triggers for safety reasons when too much power is being consumed. Second, when a similar system is used it usually relies on cloud computing or external services. In contrast our system offers the functionalities already described and both computing and data storage are done locally. This can be an advantage in terms of both privacy and security. Furthermore, this is in advantage in terms of reliability: our system doesn't need an internet connection to properly work, instead it just needs a working WLAN. However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and security issues will be discussed in the appropriate section. The architecture of the system is such that if need be it can be easily modified to use third party services.

>>>>

\begin{IEEEkeywords}
Domotic plugs; Reliable UDP; ADD MORE
\end{IEEEkeywords}

@@

\section{General architecture}
The architecture implemented differs from the most common architectures used in this scenario in two major aspects, first most homes don't have this kind of system even in place, instead a circuit breaker triggers for safety reasons when too much power is being consumed. Second, when a similar system is used it usually relies on cloud computing or external services. In contrast our system offers the functionalities already described and both computing and data storage are done locally. This can be an advantage in terms of both privacy and security. Furthermore, this is in advantage in terms of reliability: our system doesn't need an internet connection to properly work, instead it just needs a working WLAN. However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and some issues will be discussed in the appropriate section. The architecture of the system is such that if need be it can be easily modified to use third party services.

The general architecture has 3 main components: the smart plugs, an UDP server, the web interface.

The smart plugs have been prototyped using Arduino. The module drives a sensor, needed to gather data on the power consumption and communicates with the UDP server 
